Using gringo, clingo and iclingo \\\small{Rev.\svnInfoRevision}

### 2008-10-06 doc/documentation/paper.tex
added --syntax option, Doku: added --syntax, fixed aggregate bug, TODO: corrent homepage url
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/trunk/gringo@508 3e02f596-3131-0410-8352-e04eeaec37cc
DOKU: updated documentation, all authors named, fixed bug in Conjunctor
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/trunk/gringo@522 3e02f596-3131-0410-8352-e04eeaec37cc
updated outdated warnings
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/trunk/gringo@526 3e02f596-3131-0410-8352-e04eeaec37cc

\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[all]{xy}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{color}
\usepackage[nofancy]{svninfo}
\usepackage{comments}

\author{Max Ostrowski}
\title{Using gringo, clingo and iclingo
\\\small{Rev.\svnInfoRevision}
}
\date{\today}

\begin{document}
\svnInfo $Id$
\maketitle
\begin{center}\stamp\end{center}
%\includecomment{comment}
%\excludecomment{notthisone}

@@

\paragraph{Conjunctor ;}
The conjunctor ``;'' will create a conjunction of its elements.
Used in the head of a rule means that the rule is duplicated.
If used in the body instead, the atoms will be logically combined using a conjunction.
\begin{verbatim}
 a(X;1..2) :- b(X;a;b).
 b(foo). b(bar).
\end{verbatim}
will results in the rules\footnote{gringo would simplify the grounded rules since some literals in the body are facts}
\begin{verbatim}
 a(foo,1) :- b(foo), b(a), b(b).
 a(foo,2) :- b(foo), b(a), b(b).
 a(bar,1) :- b(bar), b(a), b(b).
 a(bar,2) :- b(bar), b(a), b(b).
\end{verbatim}
The conjunctor can not be used directly in aggregates, but for example in combination with the expander.
\begin{verbatim}
 { a(X,Y) : p(X;Y) }.
 p(1..2).
\end{verbatim}
Results in
\begin{verbatim}
 {a(1,1), a(1,2), a(2,1), a(2,2)}.
 p(1).
 p(2).
\end{verbatim}

@@

\paragraph{Aggregates}
An aggregate is a set or a multiset of atoms and has a lower and an upper bound.
The general syntax is
\begin{verbatim}
 lower aggregate_name [atom1=w1, ..., atomN=wN] upper
\end{verbatim}
If squared brackets are used, the atom list is interpreted as a multiset, otherwise, for curly brackets, as a set of atoms.
The lower and upper bound is optional, and can be omitted. The supported aggregates are
\begin{verbatim}
 0 count {a, b, not c} 2.
 1 sum {a=1, b=3, not c=-2} 2.
 0 max {a=1, b=2, not c=3} 5.
 1 min {a=2, b=4, not c=1} 3.
\end{verbatim}
and are now explained in detail.

@@

\paragraph{\texttt{--help,-h}}
Gives a short overview of all parameters.
\paragraph{\texttt{--version,-v}}
Prints the version information and exists.
\paragraph{\texttt{--verbose,-V}}
Prints additional information during processing.
\paragraph{\texttt{--stats}}
Prints extended statistic information.

@@

\begin{itemize}
 \item 
\begin{verbatim}
 "Warning: sum with negative bounds in the body of a rule"
\end{verbatim}
This warning occurs if a sum aggregate with negative weights has been found and the output format smodels is used or the output is redirected to clasp. In this format negative bounds are compiled away using the transformation described in \cite{lparseManual}. This may lead to counterintuitive results.
 \item 
\begin{verbatim}
 "Warning: multiple definitions of #const n"
\end{verbatim}
This warning is printed if more than one \#const statement is used to set the same constant.
The last attached value is used for grounding.
\item
\begin{verbatim}
 "Warning: p/3 is never defined"
\end{verbatim}
This warnings states that an atom is used in the body of a rule that never occurs in the head.
The predicate literal is given in the warning. The predicate will be removed through optimization.
\item
\begin{verbatim}
 "got ground program i hope u have enough memory :)"
\end{verbatim}
Use the command line option ``--ground'' to convert a ground program into another format.
For converting already ground programs to an output language a special module has been implemented that uses far less memory. Because trying to ground an already variable free program could need a huge amount of memory.
\item
\begin{verbatim}
 "Warning: There are no #base, #lambda or #delta sections."
\end{verbatim}
If writing an incremental program, the incremental sections\ref{metasyntaxinc} have to be used.
\item
\begin{verbatim}
 "Warning: There are statements not within a #base, #lambda"
 "         or #delta section."
 "         These Statements are put into the #base section."
\end{verbatim}
If writing an incremental program, all statements that are not written in an incremental section are automatically considered to belong to the \texttt{base} part of the program.
\item
\begin{verbatim}
 "Warning: Classical negation is not handled correctly in"
 "         combination with the incremental output."
 "         You have to add rules like:"
 "         :- a, -a. on your own! (at least for now)"
\end{verbatim}
To use classical negation in an incremental program the described rules have to be added manually. This will be fixed in a later version of gringo.
\end{itemize}
Furthermore all warnings from clasp are included.

>>>>

\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[all]{xy}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{color}
\usepackage[nofancy]{svninfo}
%\usepackage{comments}

\author{Martin Gebser, Roland Kaminski, Benjamin Kaufmann,\\ Max Ostrowski, Torsten Schaub, Sven Thiele}
\title{Using gringo, clingo and iclingo
\\\small{Rev.\svnInfoRevision}
}
\date{\today}

\begin{document}
\svnInfo $Id$
\maketitle
%\begin{center}\stamp\end{center}
%\includecomment{comment}
%\excludecomment{notthisone}

@@

\paragraph{Conjunctor ;}
The conjunctor ``;'' will create a conjunction of its elements.
Used in the head of a rule means that the rule is duplicated.
If used in the body instead, the atoms will be logically combined using a conjunction.
\begin{verbatim}
 a(X;1..2) :- b(X;a;b).
 b(foo). b(bar).
\end{verbatim}
will results in the rules\footnote{gringo would simplify the grounded rules since some literals in the body are facts}
\begin{verbatim}
 a(foo) :- b(foo), b(a), b(b).
 a(bar) :- b(foo), b(a), b(b).
 a(1)   :- b(bar), b(a), b(b).
 a(2)   :- b(bar), b(a), b(b).
\end{verbatim}
The conjunctor can not be used directly in aggregates, but for example in combination with the expander.
\begin{verbatim}
 { a(X,Y) : p(X;Y) }.
 p(1..2).
\end{verbatim}
Results in
\begin{verbatim}
 {a(1,1), a(1,2), a(2,1), a(2,2)}.
 p(1).
 p(2).
\end{verbatim}

@@

\paragraph{Aggregates}
An aggregate is a set or a multiset of atoms and has a lower and an upper bound.
The general syntax is
\begin{verbatim}
 lower aggregate_name [atom1=w1, ..., atomN=wN] upper
\end{verbatim}
If squared brackets are used, the atom list is interpreted as a multiset, otherwise, for curly brackets, as a set of atoms.
The lower and upper bound is optional, and can be omitted. The supported aggregates are
\begin{verbatim}
 0 count {a, b, not c} 2.
 1 sum [a=1, b=3, not c=-2] 2.
 0 max [a=1, b=2, not c=3] 5.
 1 min [a=2, b=4, not c=1] 3.
\end{verbatim}
and are now explained in detail.

@@

\paragraph{\texttt{--help,-h}}
Gives a short overview of all parameters.
\paragraph{\texttt{--version,-v}}
Prints the version information and exists.
\paragraph{\texttt{--verbose,-V}}
Prints additional information during processing.
\paragraph{\texttt{--syntax}}
Prints a short description of the syntax of the input language.
\paragraph{\texttt{--stats}}
Prints extended statistic information.

@@

\begin{itemize}
 \item 
\begin{verbatim}
 "Warning: sum with negative bounds in the body of a rule"
\end{verbatim}
This warning occurs if a sum aggregate with negative weights has been found and the output format smodels is used or the output is redirected to clasp. In this format negative bounds are compiled away using the transformation described in \cite{lparseManual}. This may lead to counterintuitive results.
 \item 
\begin{verbatim}
 "Warning: multiple definitions of #const n"
\end{verbatim}
This warning is printed if more than one \#const statement is used to set the same constant.
The last attached value is used for grounding.
\item
\begin{verbatim}
 "Warning: p/3 is never defined"
\end{verbatim}
This warnings states that an atom is used in the body of a rule that never occurs in the head.
The predicate literal is given in the warning. The predicate will be removed through optimization.
\item
\begin{verbatim}
 "got ground program i hope u have enough memory :)"
\end{verbatim}
Use the command line option ``--ground'' to convert a ground program into another format.
For converting already ground programs to an output language a special module has been implemented that uses far less memory. Because trying to ground an already variable free program could need a huge amount of memory.
\item
\begin{verbatim}
 "Warning: There are no #base, #cumulative or #volatile sections."
\end{verbatim}
If writing an incremental program, the incremental sections\ref{metasyntaxinc} have to be used.
\item
\begin{verbatim}
 "Warning: There are statements not within a #base, #cumulative"
 "         or #volatile section."
 "         These Statements are put into the #base section."
\end{verbatim}
If writing an incremental program, all statements that are not written in an incremental section are automatically considered to belong to the \texttt{base} part of the program.
\item
\begin{verbatim}
 "Warning: Classical negation is not handled correctly in"
 "         combination with the incremental output."
 "         You have to add rules like:"
 "         :- a, -a. on your own! (at least for now)"
\end{verbatim}
To use classical negation in an incremental program the described rules have to be added manually. This will be fixed in a later version of gringo.
\end{itemize}
Furthermore all warnings from clasp are included.
